How do we copy and paste? The semantic drift of quotations in blogspace

### 2015-03-10 brains-introduction.tex
Also cite Kleinberg on emails

Another research stream deals with rather macroscopic studies of knowledge diffusion. Here, one of the focal points is that not all knowledge gets propagated identically along the same routes, within the same communities, at the same pace. The various approaches usually feature a minimalistic description of cognitive processes, strongly reminiscent of biological epidemiology (a single, atomic piece of information may or may not be adopted by each individual).
This research program nonetheless exhibits a particularly interesting empirical track record --- largely owing to a recent avalanche of observable \emph{in vivo} data which, for a good decade now, have mainly come from online interaction contexts.
While these information trails are not records of ``physical'' inter-individual interactions (in the sense of ``real life'' interactions), they still constitute a wealth of observations on the dynamics of public --~albeit online~-- representations.
Some authors could describe for instance the propagation of cultural artifacts across social networks such as blogspace~\citep{Gruhl04}, the characteristic times and diffusion cycles both within these social networks and with respect to the topical dynamics of news media~\citep{Leskovec09}, or the reciprocal influence between the social network topology and the distribution of issues~\citep{Cointet09}.

>>>>

Another research stream deals with rather macroscopic studies of knowledge diffusion. Here, one of the focal points is that not all knowledge gets propagated identically along the same routes, within the same communities, at the same pace. The various approaches usually feature a minimalistic description of cognitive processes, strongly reminiscent of biological epidemiology (a single, atomic piece of information may or may not be adopted by each individual).
This research program nonetheless exhibits a particularly interesting empirical track record --- largely owing to a recent avalanche of observable \emph{in vivo} data which, for a good decade now, have mainly come from online interaction contexts.
While these information trails are not records of ``physical'' inter-individual interactions (in the sense of ``real life'' interactions), they still constitute a wealth of observations on the dynamics of public --~albeit online~-- representations.
Some authors could describe for instance the propagation of cultural artifacts across social networks such as blogspace~\citep{Gruhl04} or the email network~\citep{Liben-Nowell25032008}, the characteristic times and diffusion cycles both within these social networks and with respect to the topical dynamics of news media~\citep{Leskovec09}, or the reciprocal influence between the social network topology and the distribution of issues~\citep{Cointet09}.
